\subsubsection{The Group of Holomorphic Automorphisms on \texorpdfstring{\(\mathbb{C}\)}{the complex plane}}
In complex analysis, three main sets of interest are \(\mathbb{D}\), \(\mathbb{C}\), and \(\extcomplex\). We will now find \(\Aut(\mathbb{C})\).
\begin{theorem}[The Holomorphic Automorphism Group on \(\mathbb{C}\)]\label{thm:holomorphicautomorphismgrouponcomplexplane}
    \(\forall f\in \Aut(\mathbb{C})\), \(f\) is linear and non-constant. In other words, \(\exists a\in\mathbb{C}^*=\mathbb{C}\setminus\cbraces{0}\) and \(\exists b\in\mathbb{C}\) such that \[f(z)=az+b.\]
\end{theorem}
\begin{proof}
    First, assume that \(\infty\) is not an essential singularity of \(f(z)\) (we will prove this later). Then \(\infty\) must be a pole by trichotomy, as a removable singularity implies boundedness (\cref{prop:removablesingularityatinftyentireconstant}). Therefore, \(f(z)\) is a polynomial of degree \(m\), where \(m\in\mathbb{N}\).

    Since \(f^{-1}\in\Aut(\mathbb{C})\), it is true that \(\qty(f^{-1})'\) is entire. Since \(\qty(f^{-1})'=\frac{1}{f'\qty(f^{-1})}\), it follows that \(f'\) has no zeros in \(\mathbb{C}\). By the Fundamental Theorem of Algebra (\cref{thm:fundamentaltheoremofalgebra}), if \(m>1\), then \(f'\) has a complex zero, which is a contradiction. Hence, \(f\) must be linear, and all functions in \(\Aut(\mathbb{C})\) are in the form of \(az+b\), where \(a\in\mathbb{C}^*\), \(b\in\mathbb{C}\) are constants. In other words, any holomorphic automorphism on \(\mathbb{C}\) is a composition of a rotation, a dilation, and a translation.

    We will now prove the primary assumption; the singularity at \(z=\infty\) cannot be an essential singularity of \(f(z)\). Let \(w\in\mathbb{C}\) be arbitrary. Then by the Casorati--Weierstrass Theorem (\cref{thm:casoratiweierstrass}), \(\forall\varepsilon>0\), \(\forall R>0\), \(\exists \abs{z}>R\) such that \(|f(z)-w|<\varepsilon\). Equivalently, \(\forall R>0\), \(\exists\zeta\in D(w,\varepsilon)\) such that \(\abs{f^{-1}(\zeta)}>R\). Since \(f^{-1}\) is continuous on \(\overline{D(w,\varepsilon)}\) by holomorphy, by \cref{thm:continuousfunctionboundedoncompact}, it is bounded, which is a contradiction.
\end{proof}