\subsection{Analytic Capacity}
The theory of rational approximation is essentially built upon the concept of \textit{analytic capacity}, which was introduced in 1940 by Finnish mathematician Lars Ahlfors. Our purpose here is to give a brief and elementary introduction. Despite its importance, still many trivially simple results remain conjecture.

The uses of analytic capacity are present in many other topics of complex analysis. Analytic capacity serves as a natural framework for general rational approximation theory. Our purpose here is to hint at how analytic capacity theory relates to the proof of \cref{thm:mergelyan} and pertinent problems in general.
\begin{definition}[Analytic Capacity]\label{def:analyticcapacity}
    Let \(K\subset\mathbb{C}\) be compact. The \textit{analytic capacity} of \(K\) is defined as \[\gamma(K)=\sup\cbraces{\abs{f'(\infty)}:f\text{ is holomorphic on \(\extcomplex\setminus K\)}\wedge f(\infty)=0\wedge f\qty(\extcomplex\setminus K)\subseteq\overline{\mathbb{D}}},\] where \(f'(\infty)\) is defined as in \cref{eq:derivativeatinfinity}. For an arbitrary set \(U\subseteq\mathbb{C}\), we define \[\sup\cbraces{\gamma(K)}{K\subseteq U:K\text{ is compact}}.\]
\end{definition}
Intuitively, \(\gamma\) measures the extent to which bounded analytic functions outside \(K\) can deviate from constancy. Generally, the ``larger'' \(K\) is, the greater the capacity is.
\begin{proposition}
    If \(K\subset\mathbb{C}\) is a compact set of discrete points, then \(\lambda(K)=0\).
\end{proposition}
\begin{proof}
    For any \(f:\extcomplex\setminus K\to\mathbb{C}\) holomorphic with \(f\qty(\extcomplex\setminus K)\subseteq\overline{\mathbb{D}}\), since \(f\) is bounded, the Riemann's Theorem for removable singularities (\cref{thm:riemannremovablesingularities}) allows for an analytic continuation onto all of \(\extcomplex\). Then Liouville's Theorem (\cref{thm:liouville}) implies that \(f\) is constant and \(f'(\infty)=0\). Hence \(\gamma(K)=0\).
\end{proof}
\begin{theorem}\label{thm:analyticcapacitymonotonicity}
    For \(K_1\subseteq K_2\) both compact in \(\mathbb{C}\), \(\gamma\qty(K_1)\leq\gamma\qty(K_2)\).
\end{theorem}
\begin{proof}
    This follows directly from the definition and the fact that any function holomorphic on \(\extcomplex\setminus K_1\) is also holomorphic on \(\extcomplex\setminus K_2\).
\end{proof}
The preceding results above hint at the monotonous behavior of capacity. However, currently it is not known whether a general \textit{subadditivity} property holds for analytic capacity, or that \[\gamma\qty(K_1\cup K_2)\mathrel{\overset{?}{\leq}}\gamma\qty(K_1)+\gamma\qty(K_2).\]
Recent results hint the affirmative, as many special cases of the relation have been proved; the question of subadditivity has been proved in the affirmative for disjoint compact continua, and recent findings by Xavier Tolsa show that capacity is (countably) semi-(sub)additive (the existence of an absolute constant \(C\) such that \(\gamma\qty(K_1\cup K_2)\leq C\qty[\gamma\qty(K_1)+\gamma\qty(K_2)]\)).

We now give some quantifying examples of how analytic capacity measures a type of ``largeness'' of compact sets, (rather much like area, which satisfies the subadditivity relation). First we define a specific classification of compact sets.

A compact set \(K\subset\mathbb{C}\) is a \textit{continuum} if it is connected, \(\mathbb{C}\setminus K\) is connected, and if it is not a singleton (\(K\) contains at least 2 distinct points).
\begin{proposition}\label{prop:analyticcapacitycontinuumbiholomorphism}
    Let \(K\subset\mathbb{C}\) be a continuum. Then \(\gamma(K)=\abs{f'(\infty)}\) where \(f:\extcomplex\setminus K\to\mathbb{D}\) is a biholomorphism satisfying \(f(\infty)=0\) (or that the maximal \(\abs{f'(\infty)}\) is attained when \(f\) is biholomorphic).
\end{proposition}
\begin{proof}
    Let \(f\) be the biholomorphism, \(g:\extcomplex\setminus K\to\mathbb{D}\) be holomorphic (not necessarily surjective) mapping \(\infty\) to 0. Since \(h\equiv g\circ f^{-1}:\mathbb{D}\to\mathbb{D}\) and maps 0 to 0, the Schwarz Lemma (\cref{lem:schwarz}) implies that \[\abs{h(z)}\leq\abs{z}\] for all \(z\in\mathbb{D}\). Thus, \(\abs{g(z)}\leq\abs{f(z)}\), and \[\abs{g'(\infty)}=\lim_{z\to\infty}\abs{zg(z)}\leq\lim_{z\to\infty}\abs{zf(z)}=\abs{f'(\infty)}.\qedhere\]
\end{proof}
\begin{proposition}\label{prop:analyticcapacitycloseddisk}
    The analytic capacity of any closed disk is the radius.
\end{proposition}
\begin{proof}
    Since \(\overline{D(a,r)}\) is a continuum, a biholomorphism \(f:\extcomplex\setminus\overline{D(a,r)}\to\mathbb{D}\) such that \(f(\infty)=0\). One such biholomorphism is given by \[f(z)=\frac{r}{z-a},\qquad f'(\infty)=\lim_{z\to 0}\dv{}{z}\qty(\frac{r}{\frac1z-a})=r.\]
    Hence, \cref{prop:analyticcapacitycontinuumbiholomorphism}, gives that \(\gamma\qty(\overline{D(a,r)})=r\).
\end{proof}
\begin{proposition}\label{prop:analyticcapacitycontinuuminequalities}
    If \(K\subset\mathbb{C}\) is a continuum, then \[\frac{\diam K}4\leq\gamma(K)\leq\diam K.\]
\end{proposition}
\begin{proof}
    Assume \(f:\extcomplex\setminus K\to\mathbb{D}\) is a biholomorphism mapping \(\infty\) to 0. The lower bound follows directly from \cref{prop:complementbiholomorphismquarterestimate}. Let \(p\in K\) be arbitrary, then for any \(q\in K\), we obtain \(\abs{p-q}\leq\diam K\), implying that \(K\subseteq\overline{D\qty(p,\diam K)}\). By \cref{prop:analyticcapacitycloseddisk}, we have \(\gamma\qty(\overline{D\qty(p,\diam K)})=\diam K\), and \cref{thm:analyticcapacitymonotonicity} consequently gives the upper bound of \[\gamma(K)\leq\diam K.\qedhere\]
\end{proof}
We outline the precise connections to rational approximation:
\begin{theorem}
    Let \(K\subset\mathbb{C}\) be compact such that \(\exists c>0\) such that \(\forall\delta>0\), \(\forall p\in\partial K\), \[\gamma\qty(D(p,\delta)\setminus K)\geq c\delta.\]
    Then \(\forall f\in C^0(K)\) holomorphic on \(\interior{K}\) can be uniformly and rationally approximated on \(K\) with poles in \(\extcomplex\setminus K\).
\end{theorem}
\begin{corollary}
    Let \(K\subset\mathbb{C}\) be compact. If the connected components \(U_j\) of \(\extcomplex\setminus K\) give the uniform existence of some \(\delta>0\) such that \(\forall j\), \(\diam U_j\geq\delta\), then \(\forall f\in C^0(K)\) holomorphic on \(\interior{K}\) can be uniformly and rationally approximated on \(K\) with poles in \(\extcomplex\setminus K\).
\end{corollary}
Notice here that no restrictions are imposed on the finiteness of the number of connected components of the complement. The general conclusion given for Mergelyan's Theorem is not true for more general compact sets.

The counterexample we now provide due to~\cite{gamelin2001}, we provide the construction of the compact set \(K\).
\begin{example}
    There exists a compact set \(K\subset\mathbb{C}\) and \(f\in C^(K)\), such that \(f\) cannot be rationally approximated on \(K\). 
\end{example}
\begin{proof}
    Begin with \(\overline{\mathbb{D}}\) and let \(S=\qty{s_k}_{k\in\mathbb{N}}\) be a countably dense set of points in \(\mathbb{D}\). 

    Fix \(0<\varepsilon<1\). Let \(z_1=s_1\) and \(r_1=\frac\varepsilon2<\varepsilon\), \(r_1^2<1\). For each \(k\in\mathbb{N}\), let \(z_k\) be the first to be the first point in the dense sequence \(S\) such that \[c_k\notin\bigcup_{j=1}^{k-1}\overline{D\qty(z_j,r_j)}.\]
    Then choose \(r_k\) such that \(D\qty(z_k,r_k)\) does not intersect any previous \(D\qty(z_j,r_j)\) for \(j<k\) (possible by the fact that each \(z_j\) does not lie on the boundary of the previous disks) and so that \[r_k\leq\frac\varepsilon2-\frac12\sum_{j=1}^{k-1}r_j>0.\] Under the inductive hypothesis that \(\sum_{j=1}^{k-1}r_j<\varepsilon\), we now have \(\sum_{j=1}^{k}r_j<\varepsilon\). Apply another bound, so that \[r_k^2\leq\frac12-\frac12\sum_{j=1}^{k-1}r_j^2>0.\] Under the additional hypothesis that \(\sum_{j=1}^{k-1}r_j^2<1\), we then have that \(\sum_{j=1}^kr_j^2<1\). Define \[K=\overline{\mathbb{D}}\setminus\bigcup_{j=1}^\infty D\qty(z_j,r_j).\]
\end{proof}