%
\subsubsection{Functions Sharing Values}
In Nevanlinna's explanation of the various applications of the Second Fundamental Theorem, he proved:
\begin{theorem}[\textsc{Nevanlinna's Five-Value Theorem}]
    Let \(f_1,f_2\) be two meromorphic, admissible functions on \(D(0,R_0)\) (\(R_0<\infty\)). For each \(a\in\extcomplex\), let \(E_1(a)=\cbraces{z}{f_1(z)=a}\), \(E_2(a)=\cbraces{z}{f_2(z)=a}\). Then if \(E_1(a)\equiv E_2(a)\) for at least five different values\footnote{The compared sets are allowed to be empty (in this case both functions omit \(a\)), and we do not consider the multiplicities at each potential solution. For instance, for \(f_1(z)=z\) and \(f_1(z)=z^2\), 0 is a shared value.} of \(a\in\extcomplex\), then \(f_1\equiv f_2\).

    If \(f_1,f_2\) are two merely meromorphic (not necessarily admissible) functions on \(\mathbb{C}\) and if \(E_1(a)\equiv E_2(a)\) for at least five different values of \(a\in\extcomplex\), then either \(f_1\equiv f_2\) everywhere or they are both constant.
\end{theorem}
\begin{proof}
    Assume that five values \(a_1\) to \(a_5\) exist for which \(E_1\qty(a_1)=E_2\qty(a_1),\ldots E_1\qty(a_5)=E_2\qty(a_5)\). Without loss of generality, assume they are finite (otherwise a Möbius transformation can be utilized to map a value outside these five to the infinity point).

    Because \[\overline{N}\qty(r,a_\nu,f_1)=\overline{N}\qty(r,a_\nu,f_2)\] for \(\nu=1,\dots,5\), \(0<r<R_0\), quantify this value by \(N_\nu(r)\). We now assume that \(f_1\not\equiv f_2\). Now each shared value corresponds to an infinity of \(\Psi=\tfrac1{f_2-f_1}\).

    Now assuming that \(f_1\), \(f_2\) are not identically equal, we have \[\sum_{\nu=1}^5 N_\nu(r)\leq N(r,\Psi)\leq T(r,\Psi)=T(r,f_2-f_1)+\order{1}\leq T(r,f_1)+T(r,f_2)+\order{1}\] trivially by the First Fundamental Theorem (\cref{thm:nevanlinnafirstfundamentaltheorem}) and the properties of the characteristic. Applying \cref{eq:deficiencyrelation_fundamentalinequality} gives
    \begin{align*}
        4T\qty(r,f_j)-S\qty(r,f_j)&\leq\overline{N}\qty(r,f_j)+\sum_{\nu=1}^5N_\nu(r)-N_0\qty(r,0,f_j'),\qquad j=1,2,\\
        3T(r,f_j)&\leq S\qty(r,f_j)+\sum_{\nu=1}^5N_\nu(r).
    \end{align*}
    Summing this inequality for both values of \(j\) and applying the upper bound gives
    \begin{align*}
        T\qty(r,f_1)+T\qty(r,f_2)&\leq\tfrac13\qty[S\qty(r,f_1)+S\qty(r,f_2)]+\tfrac23\sum_{\nu=1}^5N_\nu(r)\\
        &\leq\tfrac13\qty[S\qty(r,f_1)+S\qty(r,f_2)]+\tfrac23\qty[T\qty(r,f_1)+T\qty(r,f_2)]+\order{1}.
    \end{align*}
    If \(R_0<\infty\), then outside a set \(E_0\) of logarithmic measure not exceeding 4, or \(\textstyle\int_{E_0}\frac{\dd{r}}{R_0-r}\leq 4\), by the Second Fundamental Theorem estimates (\cref{thm:nevanlinnasecondfundamentaltheorempart2}) and the fact that \(\logp T(r,f)=o\qty[T(r,f)]\), \[\qty(1-o(1))\qty[T\qty(r,f_1)+T\qty(r,f_2)]\leq\order{\log\frac1{R_0-r}}\implies\limsup_{\substack{r\to R_0^-\\r\notin E_0}}\frac{T(r,f_j)}{\log\frac1{R_0-r}}=\order{1}.\]
    We now aim to extend this outside of \(E_0\).

    For any \(r^*\in E_0\), let \(r'\in\qty{r_n}\) be the infimum of values exceeding \(r^*\) not in \(E_0\). If \(r^*=r'\), then arbitrarily close to \(r^*\), there are points for which the limit superior assertion holds. By continuity, this holds at \(r^*\) as well.

    Hence, assume \(r'>r^*\). Then \([r^*,r_n)\subseteq E_0\), we must have \(\textstyle\int_{r^*}^{r_n}\frac{\dd{r}}{R_0-r}=\log\frac{R_0-r^*}{R_0-r'}\leq 4\), so \(\log\tfrac1{R_0-r^*}\geq\log\tfrac1{R_0-r'}-4\). Since \(\log\tfrac1{R_0-r}\) is continuous and non-vanishing for \(r\) sufficiently close to \(R_0\) and \(T\) is non-decreasing, \[\frac{T\qty(r^*,f_j)}{\log\frac1{R_0-r^*}}\leq\frac{T\qty(r',f_j)}{\log\frac1{R_0-r'}}\qty(1+\frac4{\log\frac1{R_0-r'}-4})=\order{\frac{T\qty(r',f_j)}{\log\frac1{R_0-r'}}}.\]
    This shows that \[\limsup_{r\to R_0^-}\frac{T(r,f_j)}{\log\frac1{R_0-r}}=\order{1},\]
    which contradicts the admissibility of \(f_j\). Hence, our original assumption that \(f_1\not\equiv f_2\) is false, completing the first statement of the theorem.

    On the other hand, if \(R_0=\infty\), then outside a set \(E_0\) of linear measure not exceeding 4, by the Second Fundamental Theorem estimates (\cref{thm:nevanlinnasecondfundamentaltheorempart2}), \(S\qty(r,f_j)=o\qty[T\qty(r,f_j)]\), and thus \[T\qty(r,f_1)+T\qty(r,f_2)\leq o\qty[T\qty(r,f_1)]+o\qty[T\qty(r,f_2)]+\order{1}\implies T\qty(r,f_1)+T\qty(r,f_2)=\order{1}.\]
    Then \(f_1,f_2\) are constant, or the assumption that \(f_1\not\equiv f_2\) was false. This concludes the theorem.
\end{proof}
\begin{remark}
    The functions \(f_1:z\mapsto\exp\qty(z)\) and \(f_2:z\mapsto\exp\qty(-z)\) imply that five cannot be sharpened to four. Indeed, \(E_1(0)=E_2(0)=\emptyset=E_1(\infty)=E_2(\infty)\), \(E_1(1)=E_2(1)=\qty{2\uppi\ii k}_{k\in\mathbb{Z}}\), and \(E_1(-1)=E_2(-1)=\qty{2\uppi\ii k+\uppi\ii}_{k\in\mathbb{Z}}\). It can be verified algebraically that \(0,\infty,1,-1\) are the only ``shared'' values; the first two are omitted values while any solution must satisfy \(\ee^{2z}=1\), which corresponds to points where \(\exp\) attains \(1\) and \(-1\).
\end{remark}
%admissibility generalization?
